\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.5in, top=0.45in, bottom=0.45in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{array}
\usepackage{ragged2e}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.2em,itemsep=1.5pt,topsep=3pt,parsep=0pt}

\definecolor{rulegray}{HTML}{D9D9D9}
\definecolor{textgray}{HTML}{4A4A4A}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}
\titlespacing*{\section}{0pt}{8pt}{4pt}

\newcommand{\resheading}[1]{%
  \section*{#1}
  \vspace{-0.4em}\hrule height 0.6pt \vspace{0.45em}
}

\newcommand{\roleline}[4]{%
  {\bfseries #1}\hfill #2\\
  {\itshape #3}\if\relax\detokenize{#4}\relax\else, {\itshape #4}\fi\\
}

\begin{document}

\begin{center}
    {\fontsize{22}{24}\selectfont\bfseries Rouben Ghambaryan}\\[5pt]
    Los Angeles, CA \textbullet{} RoubenRG@gmail.com \textbullet{} (440) 440 1440\\[3pt]
    \href{https://www.linkedin.com/in/rouben-ghambaryan/}{linkedin.com/in/rouben-ghambaryan} \textbullet{} \href{https://rouben.dev}{rouben.dev}
\end{center}

\resheading{Skills}

\textbf{Languages:} Python, JavaScript, TypeScript, PHP, SQL \\[3pt]
\textbf{Frontend:} React, Next.js, Vue.js, Tailwind CSS, Framer Motion, Vite, Electron \\[3pt]
\textbf{Backend:} Node.js, Express, FastAPI, Zend Framework, Apache, Nginx \\[3pt]
\textbf{Cloud \& Infrastructure:} Linux, AWS (EC2, Route 53, Elastic IPs, load balancers), Docker, Kubernetes, SSH \\[3pt]
\textbf{Databases:} PostgreSQL, MariaDB, MongoDB, Redis, sql.js (WASM SQLite) \\[3pt]
\textbf{AI \& APIs:} Google Gemini API, OpenAI API, SSE streaming, REST APIs, Airtable API, Dropbox API \\[3pt]
\textbf{DevOps:} Git, CI/CD pipelines, Docker multi-stage builds, Traefik, Dokploy, DNS management, SSL lifecycle \\[3pt]
\textbf{Automation:} Selenium, data scraping pipelines, PDF parsing, document processing, browser automation

\resheading{Experience}

\roleline{Senior Software Engineer}{2023 to Present}{Inverselogic}{Los Angeles, CA}
\begin{itemize}
    \item Maintain and operate production infrastructure supporting 200+ client websites and web applications.
    \item Deploy and manage containerized workloads using Docker and Kubernetes across multi-server Linux environments.
    \item Develop and maintain internal CMS platforms and backend services using PHP, MariaDB, Redis, Apache, and Nginx.
    \item Deploy and support enterprise infrastructure used by Kaiser Permanente genetics laboratory systems.
    \item Manage DNS infrastructure and SSL certificate lifecycle across large client domain portfolios.
    \item Implement build and deployment automation pipelines for application releases.
    \item Diagnose and resolve production incidents across APIs, containers, databases, and distributed systems.
\end{itemize}

\vspace{0.2em}
\roleline{Founder \& Lead Engineer}{2024 to Present}{RLA Studios}{Los Angeles, CA}
\begin{itemize}
    \item Built a full-stack business operations platform consolidating lead generation, invoicing, CRM, and commission tracking into a single admin panel for a real estate videography company.
    \item Developed an automated scraping pipeline that extracts agent data from Redfin and Compass listings, enriches contact info, and syncs 1,963+ leads into a CRM with templated outreach workflows.
    \item Engineered an invoicing engine with automated PDF generation, payment tracking, and Dropbox integration.
    \item Built a commission tracking system that calculates per-job payouts across team members with automated reporting.
    \item Deployed on a VPS using Docker multi-stage builds with Traefik reverse proxy via Dokploy.
\end{itemize}

\vspace{0.2em}
\roleline{Software Engineer}{2022 to 2023}{Independent Software Development}{Los Angeles, CA}
\begin{itemize}
    \item Designed Python-based automation platforms for collecting and processing structured datasets using browser automation and external APIs.
    \item Built data pipelines that extract, normalize, and enrich datasets with contact information via third-party APIs.
    \item Developed automation workflows synchronizing processed datasets with Airtable-based CRM systems.
    \item Implemented automated document generation pipelines for invoices and operational workflows.
\end{itemize}

\resheading{Projects}

\textbf{AI Ticketing System} \textbullet{} \href{https://tickets.rouben.dev}{tickets.rouben.dev}\hfill 2024\\
Full-stack AI platform that transforms unstructured emails into structured, prioritized tickets with auto-generated task breakdowns. Five distinct AI interfaces powered by Google Gemini with SSE streaming, a wiki system with version control and chunked keyword search via in-process SQLite (sql.js), auto-organized company tracking, and AI-generated billing summaries. Multi-workspace tenant isolation, deployed as a single Docker container.\\
\textit{Tech:} React, Express, TypeScript, Google Gemini API, sql.js, SSE streaming, Docker

\vspace{0.4em}

\textbf{Infrastructure Audit Toolkit}\hfill 2026\\
Discovery and auditing toolkit that scans Linux environments to map servers, services, containers, DNS records, and SSL certificates across distributed infrastructure. Generates structured documentation for operational visibility.\\
\textit{Tech:} Python, Linux, Docker, SSH automation, DNS tooling

\resheading{Education}

\roleline{App Academy}{San Francisco, CA}{Full Stack Software Engineering}{}

\vspace{0.2em}
\roleline{University of Nevada, Las Vegas}{Las Vegas, NV}{Bachelor of Arts, Psychology}{}

\vspace{0.2em}
\roleline{College of Southern Nevada}{Las Vegas, NV}{Associate of Arts, Psychology}{}

\end{document}
